\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-10 paper/paper.tex
add threat model

\section{Threat Model}
% 0.5 page

-Censor can block arbitrary addresses (or networks), but faces a cost in doing so (collateral damage)
-Censor can know what network deploys the dark decoy station
-Censor knows the dark decoy prefixes distributed in the client, but they contain legitimate hosts
-Censor can use the client
-Censor can active probe limited sets, but cannot enumerate the entire prefix (i.e. IPv6 /32)
-Censor can active probe or (p)replay connections it suspects

>>>>

\section{Threat Model}
% 0.25 page

Our deployment model is identical to that of TapDance: we only require a passive
tap at the deploying ISP, and the ability to inject (spoofed) traffic from dark
decoy sites. However, we assume a stronger threat model for the adversary than
TapDance, as our design resists active attacks.

We assume the censor can block arbitrary IP addresses and networks, but faces a
cost in doing so if it blocks potentially useful resources. In particular, we
assume it is difficult for the censor to have complete knowledge of legitimate
addresses used, and so instead resorts to a blacklist approach to blocking
proxies and objectionable content.
Whitelists are expensive for censors to maintain and can stifle
innovation, and are rarely employed by censors.

We assume that the censor can know what network the dark decoy station(s) are
deployed in and the prefixes dark decoys are selected from, but that blocking those
networks outright brings a collateral
damage the censor is unwilling to suffer. Instead, the censor aims to identify
the addresses that are dark decoys, and block only those.

We assume the censor can use the client to register and access its own dark
decoys, but that these will not reveal the dark decoys of other users. The
censor can also actively probe addresses that it sees users accessing, but can
not enumerate the entire dark decoy prefix (e.g. a /32 IPv6 prefix contains
$2^{96} addresses$).

Finally, we assume the censor can replay or preplay any connections that it
suspects involve dark decoys (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are dark decoy ones, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgements or other packets that would normally
be ignored). We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

%-Censor can block arbitrary addresses (or networks), but faces a cost in doing so (collateral damage)
%-Censor can know what network deploys the dark decoy station
%-Censor knows the dark decoy prefixes distributed in the client, but they contain legitimate hosts
%-Censor can use the client
%-Censor can active probe limited sets, but cannot enumerate the entire prefix (i.e. IPv6 /32)
%-Censor can active probe or (p)replay connections it suspects
